---
title: "TITLE"
author: "AUTHOR"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    extra_dependencies: ["flafter"]
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
  word_document: default
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
---


# Section title




Some content. Also, you might need to install tinytex:

```{r,echo=TRUE,eval=FALSE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning = FALSE, message = FALSE, results = FALSE}
install.packages('tinytex')
tinytex::install_tinytex()
```


\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning = FALSE, message = FALSE, results = FALSE}
library(extrafont)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(socviz)
library(tidyverse)
library(gapminder)
library(rethinking)
library(modelr)
```
\normalsize


\vspace{1mm}

You can present the code if echo is TRUE.
\footnotesize
```{r,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, dev="cairo_pdf"}
ggplot(heights, aes(x= education, y = income))+
  stat_summary(fun=mean, geom="line", size = 1, color = "skyblue")+
  geom_jitter(width = 0.5,  alpha = 0.15, size = 1.5)+theme_tufte()+
  ggtitle("Example")+xlab("education")+ylab("income")+
  theme(plot.title.position = "plot")
```
\normalsize



# Section

A smaller visualisation on the left

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "left",cache=TRUE, fig.show = "hold", out.width = "50%", warning = FALSE, message = FALSE, dev="cairo_pdf"}
p <- ggplot(oecd_sum,  aes(x = year, y = diff, fill = hi_lo))

p+ geom_col() +guides(fill = FALSE)+
labs(x = NULL, y = "Difference in Years",
     title = "The US Life Expectancy Gap",
     subtitle = "Difference between US and OECD
average life expectancies, 1960-2015",
     caption = "Data: OECD. After a chart by Christopher Ingraham,
Washington Post, December 27th 2017.")+
  theme_tufte()+
  theme(plot.title.position = "plot")
```
\normalsize





\newpage

# Tasks

## Describe the problem you're addressing and why you've chosen it

## Describe the data you're using and explain how you obtained them


##  Explain what numerical questions you will be trying to answer and how they are related to the problem you're addressing

## Present at least two acceptable visualizations indicationg what answer the data might suggest

## Construct (with  prior predictive check and posterior predictive check) and visualize at least one model related to the numerical questions you're addressing.

## Clearly say what conclusions you'd like to draw and with what strength

## Consider and discuss potential sources of error



