---
title: "TITLE"
author: "AUTHOR"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    extra_dependencies: ["flafter"]
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
  word_document: default
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
---


# Section title


Some content

\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%",warning = FALSE, message = FALSE, results = FALSE}
library(extrafont)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(socviz)
library(tidyverse)
library(gapminder)
library(rethinking)
library(modelr)
```
\normalsize


\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", warning = FALSE, message = FALSE, dev="cairo_pdf"}
ggplot(heights, aes(x= education, y = income))+
  stat_summary(fun=mean, geom="line", size = 1, color = "skyblue")+
  geom_jitter(width = 0.5,  alpha = 0.15, size = 1.5)+theme_tufte()+
  ggtitle("Example of a visualisation")+xlab("education")+ylab("income")+
  theme(plot.title.position = "plot")
```
\normalsize



# Next section

Smaller visualisation


\vspace{1mm}
\footnotesize
```{r,echo=FALSE,eval=TRUE,fig.align = "left",cache=TRUE, fig.show = "hold", out.width = "50%", warning = FALSE, message = FALSE, dev="cairo_pdf"}
p <- ggplot(oecd_sum,  aes(x = year, y = diff, fill = hi_lo))

p+ geom_col() +guides(fill = FALSE)+
labs(x = NULL, y = "Difference in Years",
     title = "The US Life Expectancy Gap",
     subtitle = "Difference between US and OECD
average life expectancies, 1960-2015",
     caption = "Data: OECD. After a chart by Christopher Ingraham,
Washington Post, December 27th 2017.")+
  theme_tufte()+
  theme(plot.title.position = "plot")
```
\normalsize





\newpage

# Check list {-}

- [ ] We described the context of our problem


- [ ] We clearly stated the questions that guided our project, and why we think they are important

- [ ] We located and accessed relevant data

- [ ] We correctly described how the data set has been obtained


- [ ] we constructed at least two good looking visualisations presenting the phenomenon that we are describing

- [ ] we clearly explained what conclusions we are inclined to draw and why 

- [ ] we considered and clearly stated potential sources of errors and doubts


